Racial Force Probe

### 2024-02-15 paper/paper.qmd
file paths updated

health_data_count_by_demographics <- read_csv('data/msfp0116stt09data.csv')

@@

# Read data
health_data_count_by_demographics <- read_csv('data/msfp0116stt09data.csv')

>>>>

health_data_count_by_demographics <- read_csv(file = here("data/raw_data/msfp0116stt09data.csv"))

@@

# Read data
health_data_count_by_demographics <- read_csv(file = here("data/raw_data/msfp0116stt09data.csv"))
